Quality measure notes

### 2021-07-27 StateOfPractice/Ao-Report/16AnswersToResearchQuestions.tex
MI report - moved some words from ch 6 to ch 7

We answer this question by measuring the qualities and interviewing the developers. Section \ref{ch_results} contains our measurement results for \textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, and \textit{Visibility/Transparency}; Section \ref{sec_interview_software_qualities} shows results from the interviews for \textit{correctness}, \textit{maintainability}, \textit{understandability}, \textit{usability}, and \textit{reproducibility}.

We list some of the key points that may improve each quality as follows,
\begin{itemize}
\item \textbf{Installability}
\begin{itemize}
    \item clear instructions;
    \item automated installer;
    \item including all dependencies in the installer;
    \item avoiding heavily depending on other commercial products (e.g. Matlab);
    \item considering building a web application that needs no installation.
\end{itemize}
\item \textbf{Correctness \& Verifiability}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item two stage development process with stable release \& nightly builds;
    \item CI/CD;
    \item documents of requirements specifications and theory manuals.
\end{itemize}
\item \textbf{Reliability}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item two stage development process with stable release \& nightly builds;
    \item descriptive error messages.
\end{itemize}
\item \textbf{Robustness}
\begin{itemize}
    \item designing with exceptions and make the software failures elegant;
    \item descriptive error messages.
\end{itemize}
\item \textbf{Usability}
\begin{itemize}
    \item usability tests and interviews with end users;
    \item adjusting according to users’ feedbacks;
    \item getting started tutorials;
    \item user manuals;
    \item professional UX designs;
    \item active supports to users.
\end{itemize}
\item \textbf{Maintainability}
\begin{itemize}
    \item using GitHub;
    \item modular approach;
    \item documentation for developers, such as project plan, developer’s manual, and API documentation.
\end{itemize}
\item \textbf{Reusability}
\begin{itemize}
    \item modular approach;
    \item API documentation.
\end{itemize}
\item \textbf{Understandability}
\begin{itemize}
    \item modular approach;
    \item consistent codding style;
    \item clear comments;
    \item description of used algorithms;
    \item documentation;
    \item communication between developers and users via GitHub issues, mailing lists, forums etc.
    \item graphical user interface.
\end{itemize}
\item \textbf{Visibility/Transparency}
\begin{itemize}
    \item documents for the development process, project status, development environment, and release notes.
\end{itemize}
\item \textbf{Reproducibility}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item open-source;
    \item making data and documentation available;
    \item using open-source libraries.
\end{itemize}
\end{itemize}

>>>>

Section \ref{ch_results} contains our measurement results for \textit{Installability}, \textit{Correctness \& Verifiability}, \textit{Reliability}, \textit{Robustness}, \textit{Usability}, \textit{Maintainability}, \textit{Reusability}, \textit{Understandability}, and \textit{Visibility/Transparency}. We applied (surface) measurements to the nine qualities, and hope that the grading scores represent their current status. We believe that our assessments also revealed some of the development teams' practices addressing the qualities.

Section \ref{sec_interview_software_qualities} shows findings from the interviews for \textit{correctness}, \textit{maintainability}, \textit{understandability}, \textit{usability}, and \textit{reproducibility}. The interviewees expressed their thoughts on these five qualities. We discussed the current or past threats to them, and found out what actions they believed would improve the qualities.

### 2021-07-27 StateOfPractice/Ao-Report/17Recommendations.tex
MI report - moved some words from ch 6 to ch 7

I think the recommendations can originate from both parts - measurements and interviews.

>>>>

\section{Recommendations to Software Qualities}

We list some of the key points that may improve each quality as follows,
\begin{itemize}
\item \textbf{Installability}
\begin{itemize}
    \item clear instructions;
    \item automated installer;
    \item including all dependencies in the installer;
    \item avoiding heavily depending on other commercial products (e.g. Matlab);
    \item considering building a web application that needs no installation.
\end{itemize}
\item \textbf{Correctness \& Verifiability}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item two stage development process with stable release \& nightly builds;
    \item CI/CD;
    \item documents of requirements specifications and theory manuals.
\end{itemize}
\item \textbf{Reliability}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item two stage development process with stable release \& nightly builds;
    \item descriptive error messages.
\end{itemize}
\item \textbf{Robustness}
\begin{itemize}
    \item designing with exceptions and make the software failures elegant;
    \item descriptive error messages.
\end{itemize}
\item \textbf{Usability}
\begin{itemize}
    \item usability tests and interviews with end users;
    \item adjusting according to users’ feedbacks;
    \item getting started tutorials;
    \item user manuals;
    \item professional UX designs;
    \item active supports to users.
\end{itemize}
\item \textbf{Maintainability}
\begin{itemize}
    \item using GitHub;
    \item modular approach;
    \item documentation for developers, such as project plan, developer’s manual, and API documentation.
\end{itemize}
\item \textbf{Reusability}
\begin{itemize}
    \item modular approach;
    \item API documentation.
\end{itemize}
\item \textbf{Understandability}
\begin{itemize}
    \item modular approach;
    \item consistent codding style;
    \item clear comments;
    \item description of used algorithms;
    \item documentation;
    \item communication between developers and users via GitHub issues, mailing lists, forums etc.
    \item graphical user interface.
\end{itemize}
\item \textbf{Visibility/Transparency}
\begin{itemize}
    \item documents for the development process, project status, development environment, and release notes.
\end{itemize}
\item \textbf{Reproducibility}
\begin{itemize}
    \item test-driven development with unit tests, integration tests, nightly tests, etc.
    \item open-source;
    \item making data and documentation available;
    \item using open-source libraries.
\end{itemize}
\end{itemize}
